### 2023-04-13 my_paper/Hadah-last-names.tex
edits
...

Let $Y_{ist}$ be the annual log earnings of person $i$ at time $t$. $WH_{ist}$, $HW_{ist}$ and $HH_{ist}$ are indicator variables for the type of parents person $i$ has. $X_{ist}$ is a vector of controls, $\gamma_{t}$ are year fixed effects, $\lambda_{s}$ are state fixed effects, and $\phi_{ist}$ represents the error term. The equation for this strategy is written as follows:
\begin{equation} \label{eq:1a}
Y_{ist} = \beta_{1} WH_{ist} +\beta_{2} HW_{ist} + \beta_{3} HH_{ist} + X_{ist} \pi + \gamma_{t} + \lambda_s + \phi_{ist}
\end{equation}

@@

From equation \ref{eq:naive}, $\beta_{1}$ estimates the earnings gap between Hispanics and Whites. When calculating the equation, before controlling for education, I find an earnings gap that is equal to 15.6\%. This gap is close to the gap between HH and WW. After controlling for education, the gap decreases by more than half and becomes 6\%, which is also similar to the gap between HH and WW after controlling for education. Since the differences between Whites and Hispanics, both observable and unobservable, are large, estimating the gap HW-WH could provide us with a bound on how much of the discrimination against Hispanics is taste-based.

The point estimate of the difference between HW and WH from equation \ref{eq:1a} is equal to 1.3 percentage points. The upper bound of the confidence interval is equivalent to 4.5 percentage points. Therefore, I can put a potential upper bound on the portion of the Hispanic-White earnings gap that could be explained by taste based discrimination. In this case, the upper bound is equal to 4.5 percentage points.

>>>>

Let $Y_{ist}$ be the annual log earnings of person $i$ in state $s$ at time $t$. $WH_{ist}$, $HW_{ist}$ and $HH_{ist}$ are indicator variables for the type of parents person $i$ has. $X_{ist}$ is a vector of controls, $\gamma_{t}$ are year fixed effects, $\lambda_{s}$ are state fixed effects, and $\phi_{ist}$ represents the error term. The equation for this strategy is written as follows:
\begin{equation} \label{eq:1a}
Y_{ist} = \beta_{1} WH_{ist} +\beta_{2} HW_{ist} + \beta_{3} HH_{ist} + X_{ist} \pi + \gamma_{t} + \lambda_s + \phi_{ist}
\end{equation}

@@

From equation \ref{eq:naive}, $\beta_{1}$ estimates the earnings gap between Hispanics and Whites. When calculating the equation, before controlling for education, I find an earnings gap that is equal to 17\%. After controlling for education, the gap decreases by more than half and becomes 7\%. Since the differences between Whites and Hispanics, both observable and unobservable, are large, estimating the gap HW-WH could provide us with a bound on how much of the discrimination against Hispanics is taste-based.

The point estimate of the difference between HW and WH from equation \ref{eq:1a} is equal to 2 percentage points. The lower bound of the confidence interval is equal to 6 percentage points. Therefore, I can put a potential upper bound on the portion of the Hispanic-White earnings gap that could be explained by taste based discrimination. In this case, the upper bound is equal to 6 percentage points.
